
\documentclass{iopjournal}
\begin{document}
\articletype{Research Article}
\title{IOP Family: Official IOP Submission Preview}
\author{A. Placeholder$^1$ and B. Example$^2$}
\affil{$^1$Department of Verified Templates, Placeholder Institute, City, Country}
\affil{$^2$Journal Systems Lab, Example University, City, Country}
\email{verified@example.org}
\keywords{template verification, IOP style, manuscript preview}
\begin{abstract}
This submission-style preview is rendered with the imported official IOP journal article package. The content remains placeholder text, but the page is intentionally structured as a realistic physics-oriented manuscript so front matter, section flow, figure-table rhythm, and end sections are easier to inspect.
\end{abstract}
\section{Introduction}
The introduction is written as compact technical prose so the preview reads more like a practical IOP submission than a generic display page.
\section{Related Work}
The related-work section is explicit so the preview reveals how literature framing, methods, and experiments separate within the family baseline.
\section{Methodology}
The methodology section introduces representative notation and a figure placeholder so the imported IOP package can be inspected under more realistic technical content.
\begin{equation}
\mathcal{L} = \sum_{i=1}^{M} w_i \left\| y_i - \hat{y}_i \right\|_2^2.
\end{equation}
\section{Experiments}
The experiments section provides enough structure to expose quantitative comparison rhythm and table treatment inside the IOP family baseline.
\section{Conclusion and Discussion}
This page verifies the imported official IOP package path while preserving the six-part manuscript skeleton requested for the library.
\ack{Placeholder acknowledgment.}
\funding{Placeholder funding statement.}
\data{Placeholder data availability statement.}
\section*{References}
\begin{thebibliography}{9}
\bibitem{ref1} A. Smith and B. Lee, {\it Template-aware IOP manuscript preparation}, Placeholder Journal 1 (2026) 1--10.
\end{thebibliography}
\end{document}
